CorReg

### 2015-02-08 www/soutenance.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@1048 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\section{Context}
	\subsection{Industrial context}
		\begin{frame}
				  \begin{enumerate}
				\item Steel industry databases.
				\item Goal: To understand and prevent quality problems on finished product, knowing the whole process, \underline{without a priori}.
			\end{enumerate}
	        \begin{center}
	          \begin{tabular}{ccc}
	         \includegraphics[width=70px,height=70px]{liquid.jpg} & \includegraphics[width=70px,height=70px]{Brame1.jpg} & \includegraphics[width=70px,height=70px]{Brame.jpg} \\
	          	\includegraphics[width=70px,height=70px]{ecras_moy.jpg} & \includegraphics[width=70px,height=70px]{tcc2.jpg} & \includegraphics[width=70px,height=70px]{bobines.jpg}
	          \end{tabular}
	        \end{center}
		\end{frame}
	\subsection{Statistical context}
		\begin{frame}{Regression}
			\begin{equation}
				\boldsymbol{Y}=\boldsymbol{X}\boldsymbol{\beta} + \boldsymbol{\varepsilon}\label{regressionsimple}
			\end{equation}
			where 	$\boldsymbol{\varepsilon}\sim \mathcal{N}(0,\sigma_Y^2)$	
		\end{frame}

@@

	\begin{frame}
	\begin{figure}
	 \centering
	  \includegraphics[width=250px]{figures/MQEreel/OLScompl.png}
	  \caption{Evolution of observed Mean Squared error on $\hat{\boldsymbol{\beta}}_{OLS}$ with the strength of the correlations for various sample sizes and strength of regression. $d=5$ covariates (running example). } \label{MQEOLScompl}
	\end{figure}	
\end{frame}		
		\begin{frame}{Ridge}
		Alternative ridge : bien mais pas de sélection donc inacceptable
		\end{frame}

		\begin{frame}{Ridge}
		Alternative ridge : bien mais pas de sélection donc inacceptable
		\end{frame}

		\begin{frame}{LASSO}
		Alternative lasso (et autres) : bien mais problèmes en cas de corrélations
		\end{frame}
		\begin{frame}{LASSO}
		Liste des alternatives
		\end{frame}
		\begin{frame}{ SEM }
		 Modélisation de la structure mais à la main et aucun impact sur l'estimation
		 \end{frame}

>>>>

\section{Context}
	\subsection{Industrial context}
		\begin{frame}
				  \begin{enumerate}
				\item Steel industry databases.
				\item Goal: To understand and prevent quality problems on finished product, knowing the whole process, \underline{without a priori}.
			\end{enumerate}
	        \begin{center}
	          \begin{tabular}{ccc}
	         \includegraphics[width=70px,height=70px]{liquid.jpg} & \includegraphics[width=70px,height=70px]{Brame1.jpg} & \includegraphics[width=70px,height=70px]{Brame.jpg} \\
	          	\includegraphics[width=70px,height=70px]{ecras_moy.jpg} & \includegraphics[width=70px,height=70px]{tcc2.jpg} & \includegraphics[width=70px,height=70px]{bobines.jpg}
	          \end{tabular}
	        \end{center}
		\end{frame}
	\subsection{Statistical context}
		\begin{frame}{Regression}
			\begin{equation}
				\boldsymbol{Y}=\boldsymbol{X}\boldsymbol{\beta} + \boldsymbol{\varepsilon}\label{regressionsimple}
			\end{equation}
			where 	$\boldsymbol{\varepsilon}\sim \mathcal{N}(0,\sigma_Y^2\boldsymbol{I}_n)$	
		\end{frame}

@@

	\begin{frame}
	\begin{figure}
	 \centering
	  \includegraphics[width=250px]{figures/MQEreel/OLScompl.png}
	  \caption{Evolution of observed Mean Squared error on $\hat{\boldsymbol{\beta}}_{OLS}$ with the strength of the correlations for various sample sizes and strength of regression. $d=5$ covariates (running example). } \label{MQEOLScompl}
	\end{figure}	
\end{frame}		
		\begin{frame}{Ridge Regression}
		\cite{hoerl1970ridge,marquardt1975ridge} proposes a possibly biased estimator for $\boldsymbol{\beta}$ that can be written in terms of a parametric $L_2$ penalty:
	\begin{equation}
		 \boldsymbol{\hat{\beta}}=\operatorname{argmin}_{\boldsymbol{\beta}} \left\lbrace \parallel \boldsymbol{Y}-\boldsymbol{X\beta}\parallel_2^2 \right\rbrace \textrm{ subject to } \parallel \boldsymbol{\beta} \parallel_2^2\leq \eta \textrm{ with } \eta>0
	\end{equation}
	But this penalty is not guided by correlations. 
	The solution of the ridge regression is given by
	\begin{equation}
		 \hat{\boldsymbol{\beta}}=\left(\boldsymbol{X}'\boldsymbol{X} -\lambda\boldsymbol{I}_n\right) ^{-1}\boldsymbol{X}'\boldsymbol{Y}\label{betaridge}
	\end{equation}
 Methods do exist to automatically choose a good value for $\lambda$ \cite{cule2013ridge,er2013systematic} and a R package called {\tt ridge} is on {\sc cran} \cite{packageridge}.
		\end{frame}

		\begin{frame}{Ridge Regression}
 \begin{figure}
	 \centering
	  \includegraphics[width=250px]{figures/MQEreel/ridgecompl.png}
	  \caption{Evolution of observed Mean Squared error on $\hat{\boldsymbol{\beta}}_{ridge}$ with the strength of the correlations for various sample sizes and strength of regression. $d=5$ covariates. } \label{MQEridgecompl}
	\end{figure}
			\end{frame}

		\begin{frame}{LASSO}
		The Least Absolute Shrinkage and Selection Operator ({\sc lasso}, \cite{tibshirani1996regression} and \cite{tibshiranilasso}) consists in a shrinkage of the regression coefficients based on a $\lambda$ parametric $L_1$ penalty to obtain zeros in $\hat{\boldsymbol{\beta}}$ instead of the $L_2$ penalty of the ridge regression:
		\begin{equation}
		 \boldsymbol{\hat{\beta}}=\operatorname{argmin} \left\lbrace \parallel \boldsymbol{Y}-\boldsymbol{X\beta}\parallel_2^2 \right\rbrace \textrm{ subject to } \parallel\boldsymbol{\beta} \parallel_1\leq \lambda \textrm{ with } \lambda>0 . \nonumber 
		\end{equation}

		\end{frame}
		\begin{frame}{LASSO}
		\begin{figure}[h!]
			\centering
			\includegraphics[width=150px]{figures/lasso.png} 
			\caption{Geometric view of the Penalty for the \textsc{lasso} (left) compared to ridge regression (right) as shown in the book from Hastie \cite{hastie2009elements}} \label{lassogeom}
		\end{figure}
		Figure shows the contour of error (red) and constraint function (blue).
		  The axis stands for the regression coefficients.
		\end{frame}

\begin{frame}

		Here again we have to choose a value for $\lambda$.
	 The Least Angle Regression (\textsc{LAR} \cite{efron2004least}) algorithm offers a very efficient way to obtain the whole \textsc{lasso} path.  It can be used through the {\tt lars } package on {\sc cran} (\cite{packagelars}).
\end{frame}

\begin{frame}
 \begin{figure}
	 \centering
	  \includegraphics[width=250px]{figures/MQEreel/larcompl.png}
	  \caption{Evolution of observed Mean Squared error on $\hat{\boldsymbol{\beta}}_{lar}$ with the strength of the correlations for various sample sizes and strength of regression. $d=5$ covariates. } \label{MQElarcompl}
	\end{figure}	
\end{frame}

		\begin{frame}{ SEM }
		 Modélisation de la structure mais à la main et aucun impact sur l'estimation
		 \end{frame}
